Studying the Performance of the Jellyfish Search Optimiser for the Application of Projection Pursuit

### 2024-08-15 jso.qmd
added on prop 1

\begin{prop}\label{prop:convex-concave}
Let $g_1(d)$ be a convex function and $g_2(d)$ be a concave function, where $d \in [0, D]$ and $g_1(d), g_2(d) \in [0, 1]$. Assume both functions achieve the same maximum gradient, i.e., $\max g'_1(d_1) = \max g'_2(d_2) = -g_{max}$, it follows that $d_1 < d_2$ and $\varsigma(f_1) < \varsigma(f_2)$.
\end{prop}

>>>>

\begin{prop}\label{prop:convex-concave}
Let $g_1(d)$ be a convex decreasing function and $g_2(d)$ be a concave decreasing function defined on [0, 1] where $d \in [0, D]$. Let $d_1 := \underset{d}{\arg \max} |g_1'(d)|$ and $d_2 := \underset{d}{\arg \max} |g_2'(d)|$.

$$\varsigma(g_1) < \varsigma(g_2)$$

For a convex function, $g_1'(d) < 0 \; \forall d$ and is non-decreasing. For a concave function, $g_2'(d) < 0 \; \forall d$ and is non-increasing. As such, it follows that $d_1 < d_2$.

Suppose both functions achieve the same maximum gradient $-g_{\max}$, i.e., $\max g'_1(d_1) = \max g'_2(d_2) = -g_{\max}$,

$$
\varsigma(g_1(d_1)) = -c  \max g'_1(d_1)  d_1 = -c  (-g_{\max}) d_1 \leq -c  (-g_{\max}) d_2 = -c \max g'_2(d_2)  d_2 = \varsigma(g_2(d_2))
$$

\end{prop}

### 2024-08-15 jso.tex
added on prop 1

\begin{keyword}
    projection pursuit \sep jellyfish search optimiser
(JSO) \sep optimisation \sep grand tour \sep high-dimensional data \sep 
    exploratory data analysis
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, sharp corners, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, toptitle=1mm, opacityback=0, opacitybacktitle=0.6, bottomrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, breakable, leftrule=.75mm, colback=white, rightrule=.15mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, coltitle=black, bottomtitle=1mm, titlerule=0mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, arc=.35mm]

>>>>

\begin{keyword}
    projection pursuit \sep jellyfish search optimiser
(JSO) \sep optimisation \sep grand tour \sep high-dimensional data \sep 
    exploratory data analysis
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, breakable, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, toprule=.15mm, coltitle=black, colframe=quarto-callout-note-color-frame, breakable, colbacktitle=quarto-callout-note-color!10!white, titlerule=0mm, bottomtitle=1mm, toptitle=1mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, arc=.35mm, rightrule=.15mm, bottomrule=.15mm, left=2mm, leftrule=.75mm, opacityback=0, colback=white]
